---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/12/2019"
output: html_document
---

Display all of your answers by simply writing the variable name at the end of the code block.

Load libraries that you need
```{r setup, warning=FALSE, message=FALSE}
library("tidyverse")
library("DBI")
```

Connect to `chinook.db`
```{r}
#
```


Create variables to represent the tables: `genres, albums, artists, tracks, invoices, customers, media_types`. This will make it easier to use these tables later on.
```{r}
#
```


Who are the top 10 customers?
```{r}
#
```


Who is the top customer in each country?
```{r}
#
```


Plot the sum of `Total` from invoices by year in a line chart.
```{r}
#
```


What's the average length of a `track` for each `artist` on each `album`?
```{r}
#
```



If the different `media_types` cost different amounts of money to sell, calculate your top 10 most profitable tracks. For this example, all costs are equal EXCEPT for the `media_type`.  

COSTS:  

  - MPEG = $0.15
  - Protected MPEG-4 = $0.25
  - AAC = $0.03
  - Protected AAC = $0.10
  - Purchased AAC = $0.08
  
```{r}
#
```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes 
```{r}

```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes, `facet_wrap` by `media_type`
```{r}

```


Create a linear regression model using `milliseconds` as a predictor of `bytes`. Hint, formula: `bytes ~ milliseconds`
```{r}

```


Create a linear model using the same formula but split it out according to `media_type`
```{r}

```


Create a linear model using the same formula but split it out according to `artist`
```{r}

```

