---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/12/2019"
output: html_document
---

Display all of your answers by simply writing the variable name at the end of the code block.

Load libraries that you need
```{r setup, warning=FALSE, message=FALSE}
library("tidyverse")
library('RSQLite')
library("DBI")
library("lubridate")
```

Connect to `chinook.db`
```{r}
# 
con <- DBI::dbConnect(RSQLite::SQLite(), "chinook.db")
```


Create variables to represent the tables: `genres, albums, artists, tracks, invoices, customers, media_types`. This will make it easier to use these tables later on.
```{r}
#
genres      <- tbl(con, 'genres')
albums      <- tbl(con, 'albums')
artists     <- tbl(con, 'artists')
tracks      <- tbl(con, 'tracks')
invoices    <- tbl(con, 'invoices')
customers   <- tbl(con, 'customers')
media_types <- tbl(con, 'media_types')
```


Who are the first 10 `customers` in the database? Return only `FirstName` and `LastName`
Answer using SQL and `dbGetQuery()` (not `tbl()`)
```{r}
#
qry <- "SELECT FirstName, LastName FROM customers LIMIT(10)"
dbGetQuery(con, qry)
```


Complete the same task as above using `tbl()`
```{r}
#
firstTen <- tbl(con, 'customers') %>%
  select(FirstName, LastName)
  head(10)
firstTen
```


For the rest of the assignment, please use the `tbl()` function ... but you may use raw SQL if it is easier for you.

Count the number of `customers` by `country` and arrange in descending order.
```{r}
#
customers %>%
  group_by(Country) %>%
  count() %>%
  arrange(-n)
```


Plot the sum of `Total` from invoices by year in a line chart.
```{r}
#
invoices %>%
  mutate(year = as.Date(InvoiceDate)) %>% # extract year
  group_by(year) %>%
  summarize(yearly_total = sum(year, na.rm = TRUE)) %>%
  as_tibble() %>% # convert to proper tibble datafram fro plotting
  ggplot() +
  geom_line(aes(x=year, y=yearly_total), color ='blue')
```


What's the average length of a `track` for each `artist` on each `album`?
```{r}
#
avg_track_length <- tracks %>%
  left_join(albums, by='AlbumId') %>%
  left_join(artists, by='ArtistId') %>%
  # rename(c('Name.y' = 'Artist')) %>%
  group_by(Name.y, Title) %>% # artist, album
  summarize(
    artist=Name.y,
    length=Milliseconds,
    avg_leng=mean(Milliseconds),
    n = n()
  ) %>%
  select(artist, avg_leng)
  
avg_track_length
```



If the different `media_types` cost different amounts of money to sell, calculate your top 10 most profitable tracks. For this example, all costs are equal EXCEPT for the `media_type`.  

COSTS:  

  - MPEG = $0.15
  - Protected MPEG-4 = $0.25
  - AAC = $0.03
  - Protected AAC = $0.10
  - Purchased AAC = $0.08
  
```{r}
# Cost Vector
costs <- tribble(
  ~key, ~val,
     "MPEG audio file", .15,
     "Protected MPEG-4 video file", .25,
     "AAC audio file", .03,
     "Protected AAC audio file", .10,
     "Purchased AAC audio file", .08
)

TrackSales <- tracks %>%
  left_join(media_types, by='MediaTypeId') %>%
  rename(TrackName = Name.x) %>%
  rename(MediaTypeName = Name.y) %>%
  as_tibble()ß

mostProfitableTracks <- TrackSales %>%
  mutate(
    # select cost based on media type
    profit = UnitPrice - (costs$val[match("Protected AAC audio file", costs$key)])
  ) %>%
  arrange(-profit) %>%
  select(TrackName, profit) %>%
  head(10)

mostProfitableTracks
```


Use `tidyr` functions `spread()` or `gather()` to show data that counts the number of `artists` by `genre` looks like the following:
```{r}
# A tibble: 1 x 26
#   Alternative `Alternative & … Blues `Bossa Nova` Classical Comedy Drama `Easy Listening`
#         <int>            <int> <int>        <int>     <int>  <int> <int>            <int>
#          40              332    81           15        74     17    64               24
# … with 18 more variables: `Electronica/Dance` <int>, `Heavy Metal` <int>, `Hip Hop/Rap` <int>,
#   Jazz <int>, Latin <int>, Metal <int>, Opera <int>, Pop <int>, `R&B/Soul` <int>, Reggae <int>,
#   Rock <int>, `Rock And Roll` <int>, `Sci Fi & Fantasy` <int>, `Science Fiction` <int>,
#   Soundtrack <int>, `TV Shows` <int>, World <int>, `<NA>` <int>

```



Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes 
```{r}
tracks %>%
  as_tibble() %>%
  ggplot() +
  geom_point(aes(Milliseconds,Bytes))
```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes, `facet_wrap` by `media_type`
```{r}
tracks %>%
  left_join(media_types, by="MediaTypeId") %>%
  rename(MediaType = Name.y) %>%
  as_tibble() %>%
  ggplot() +
  geom_point(aes(Milliseconds,Bytes)) +
  facet_wrap(~MediaType)
```


Create a linear regression model using `milliseconds` as a predictor of `bytes`. Hint, formula: `bytes ~ milliseconds`
```{r}
lrdata <- tracks %>% as_tibble()
lm(Bytes ~ Milliseconds, lrdata)
```


Create a linear model using the same formula but split it out according to `media_type`
```{r}
lrdataSplit <- tracks %>% 
  left_join(media_types, by="MediaTypeId") %>%
  rename(MediaTypeName = Name.y) %>%
  group_by(MediaTypeName) %>%
  summarize(
    n = n(),
    ms = Milliseconds,
    b = Bytes
  ) %>%
  as_tibble() 

lrdataSplit

lm(b ~ ms + MediaTypeName, lrdataSplit)

```

