---
title: "Demonstration"
author: "Scott Stoltzman"
date: "6/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library('tidyverse')
library('DBI')
```

#### Establishes a connection, you can replace RSQLite with another database
```{r}
con <- DBI::dbConnect(RSQLite::SQLite(), "chinook.db")
```


#### Commands
```{r}
# Show all tables
dbListTables(con)
```


```{r}
# Select all data from genres
qry = 'SELECT * FROM genres;'
dbGetQuery(con, qry)
```


#### Tidyverse will make life easier...
```{r}
tbl(con, 'genres')
```



Easily filter data:
```{r}
tbl(con, 'genres') %>% filter(Name == 'Jazz')
```



#### How do we group albums by artist?
```{r}
tbl(con, 'albums') %>%
  left_join(tbl(con, 'artists'), by = 'ArtistId')
```

```{r}
tbl(con, 'artists')
```


Create variables for table connections for simplicity:
```{r}
artists = tbl(con, 'artists')
albums = tbl(con, 'albums')
```

Then use dplyr join to merge the two. You see ArtistId in both `albums` and `artists`
```{r}
albums %>% 
  left_join(artists, by = 'ArtistId')
```

Proceed to do your `dplyr` wrangling as normal!
```{r}
albums %>% 
  left_join(artists, by = 'ArtistId') %>%
  select(Name, Title)
```



How many albums did each artist put out? Sort this in descending order.
```{r}
albums %>% 
  left_join(artists, by = 'ArtistId') %>%
  group_by(Name) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```

What data type is this??
```{r}
what_is_this = albums %>% 
  left_join(artists, by = 'ArtistId') %>%
  group_by(Name) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
class(what_is_this)
```

So what does that mean???
```{r}
what_is_this %>% show_query()
```


It means you can have the database do the heavy lifting! Then results are easy to convert to a tibble.
```{r}
what_is_this %>% as_tibble()
```

